---
title: "Fairlabs Dashboard"
header-includes:
  - \usepackage{comment}
output:
  flexdashboard::flex_dashboard:
    css: style.css
    theme: cosmo
    orientation: rows
    vertical_layout: scroll
    source_code: embed
---
```{r, include=FALSE}
library(DT)
library(flexdashboard)
library(DBI)
library(tidyverse)
library(lubridate)
library(plotly)
library(knitr)
library(janitor)
library(reshape2)
require(scales)
library(dplyr)
library(glue)
library(broom)
library(gtsummary)
```

```{r}
data <- read.csv("/input.csv")
```
```{r}
# definitions
drup_col <- colnames((data))
non_thc_col <- drup_col[grepl('detected_', drup_col) & !grepl('tetrahydrocannabinol', drup_col)]
intervention_date <- as.Date('2028-03-01')
race_pal <- setNames(object = c("#66c2a5","#fc8d62","#8da0cb"), nm = c('Black or African American', 'White', 'Other'))
age_pal <- setNames(object = c("#f0f9e8","#bae4bc","#7bccc4", '#2b8cbe'), nm = c('Under 25', '25 - 30', '30 - 34', 'Over 34'))

# cleaning
data <- data %>% mutate(
  # date cleaning
  delivery_date = as.Date(delivery_date),
  cps_reporting_date = as.Date(cps_reporting_date),
  uds_collection_date = as.Date(uds_collection_date),
  non_thc_detect = if_else(rowSums(data[non_thc_col]) > 0, TRUE, FALSE),
  thc_detect = if_else(detected_tetrahydrocannabinol == 1, TRUE, FALSE),
  uds_test = if_else(is.na(uds_collection_date), FALSE, TRUE),
  pre_post_QI = factor(if_else(delivery_date >= intervention_date, 'Post', 'Pre'), levels = c('Pre', 'Post')),
  cps_report = if_else(is.na(cps_reporting_date), FALSE, TRUE),
  delivery_month = as.Date(format.Date(delivery_date, '%Y-%m-01')),
  # The age ranges where arbitrarily chosen which the goal of being approximately equal in size
  age_group= factor(case_when(maternal_age < 25 ~ 'Under 25', maternal_age < 30 ~ '25 - 30', maternal_age < 34 ~ '30 - 34', TRUE ~ 'Over 34'), levels=c('Under 25','25 - 30','30 - 34','Over 34')),
  # The dataset is 90% black or white, so all other values, including unspecified and multiracial values are combined into Other.
  race_group=case_when(maternal_race == 'Black or African American' ~ maternal_race, maternal_race == 'White' ~ maternal_race, TRUE ~ 'Other'),
  ord_indict_non_thc = if_else(order_indication %in% c("Substance use during pregnancy, excluding marijuana", "History of opioids prescribed during pregnancy"), TRUE, FALSE))

```

```{r}
# data summary 

## demographic parity
demo_sum <- data %>%
  group_by(race_group,age_group,pre_post_QI,delivery_month,has_order) %>%
  count() %>%
  ungroup() %>%
  group_by(race_group,age_group,pre_post_QI,delivery_month) %>%
  mutate(total = sum(n),
         perc_total = round(n/total, digits = 2)) %>%
  ungroup() 

## predictive parity
pred_non_thc_sum <- data %>%
  filter(has_order) %>%
  group_by(race_group,pre_post_QI,delivery_month,non_thc_detect) %>%
  count() %>%
  ungroup() %>%
  group_by(race_group,pre_post_QI,delivery_month) %>%
  mutate(total = sum(n),
         perc_total = round(n/total, digits = 2)) %>%
  ungroup() 

pred_thc_sum <- data %>%
  filter(has_order) %>%
  group_by(race_group,pre_post_QI,delivery_month,thc_detect) %>%
  count() %>%
  ungroup() %>%
  group_by(race_group,pre_post_QI,delivery_month) %>%
  mutate(total = sum(n),
         perc_total = round(n/total, digits = 2)) %>%
  ungroup() 

## equalized odds
equal_odds <- data %>%
  filter(has_order) %>%
  group_by(race_group,age_group,pre_post_QI,ord_indict_non_thc,non_thc_detect) %>%
  count() %>%
  ungroup() %>%
  mutate(ord_ind_detect = factor(case_when(ord_indict_non_thc & non_thc_detect ~ 'TP',
                                    ord_indict_non_thc & !non_thc_detect ~ 'FP',
                                    !ord_indict_non_thc & !non_thc_detect ~ 'TN',
                                    !ord_indict_non_thc & non_thc_detect ~ 'FN')))

equal_odds_wide <- pivot_wider(equal_odds%>%
  select(c("race_group","age_group","pre_post_QI",'ord_ind_detect', 'n')), names_from = ord_ind_detect, values_from = n) %>%
  mutate(FPR = (FP/(FP+TN)), 
         TPR = (TP/(TP+FN)), 
         ratio = FPR/TPR)

## equal outcomes
equal_out <- data %>%
  # filter(!is.na(cps_reporting_date)) %>%
  group_by(has_order, race_group, age_group, non_thc_detect,cps_report, pre_post_QI,delivery_month) %>%
  count() %>%
  ungroup() %>%
  group_by(has_order, race_group, age_group,pre_post_QI,delivery_month) %>%
  mutate(total = sum(n),
         perc_total = round(n/total, digits = 2)) %>%
  ungroup() 

## group benefit equality
group_benefit <- data %>%
  filter(uds_test) %>%
  group_by(race_group,age_group,pre_post_QI,cps_report,non_thc_detect) %>%
  count() %>%
  ungroup() %>%
  mutate(cps_detect = factor(case_when(cps_report & non_thc_detect ~ 'TP',
                                          !cps_report & non_thc_detect ~ 'FP',
                                          !cps_report & !non_thc_detect ~ 'TN',
                                          cps_report & !non_thc_detect ~ 'FN')))

group_benefit_wide <- pivot_wider(group_benefit %>%
  select(c("race_group","age_group","pre_post_QI",'cps_detect', 'n')), names_from = cps_detect, values_from = n) %>%
  mutate(ratio = ((TP+FP)/(TP+FN)))
```

```{r, child = 'visuals.rmd'}
```

Demographic Parity
==================

### Metric Description

We measure demographic parity using the portion of each demographic's subpopulation that was given drug testing.

```{r}
tab_data <- data %>% mutate(y=has_order)
```
```{r, child = 'section.rmd'}
```

Predictive Parity
=================

### Metric Description

We measure predictive parity using the portion of the population that received testing that tested positive for a drug other than other than marijuana. We measure this using a separate population for each demographic group, and define predictive parity to be the goal of equality between the measure for each group.

```{r}
tab_data <- data %>% filter(has_order) %>% mutate(y=positive_non_marijuana)
```
```{r, child = 'section.rmd'}
```