Statistics
==========================

Row
-----------------------------------------------------------------------

### Demographic Parity

We measure demographic parity using the proportion of each race and age group that was given drug testing.
<br/>**Goal**: Achieve parity in all race and age groups

Row
-----------------------------------------------------------------------

### Logistic regression model`r if_else(is.na(intervention_date), '', '- Pre Intervention')`
```{r}
# check if QI intervetion date is available
if (sum(is.na(data$pre_post_QI)) == nrow(data)) {
  glm_pre <- glm(uds_test ~ race_group + age_group, data=data, family = "binomial") %>% 
    tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                   label = list(age_group ~ "Age group",
                                race_group ~ "Race group")) %>%
    as_gt()

  div(style='height:100%; overflow-y: scroll', glm_pre)
} else {
  # if QI date not available
  glm_pre <- glm(uds_test ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Pre"), family = "binomial") %>% 
    tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                   label = list(age_group ~ "Age group",
                                race_group ~ "Race group")) %>%
    as_gt()

  div(style='height:100%; overflow-y: scroll', glm_pre)
}
```

`r if(is.na(intervention_date)) {"\\begin{comment}"}`

### Logistic regression model - Post Intervention
```{r}
if (sum(is.na(data$pre_post_QI)) == nrow(data)) {
  glm_post <- glm(uds_test ~ race_group + age_group, data=data, family = "binomial") %>% 
    tbl_regression(add_estimate_to_reference_rows=TRUE,  exponentiate = TRUE,
                   label = list(age_group ~ "Age group",
                                race_group ~ "Race group")) %>%
      as_gt()

  div(style='height:100%; overflow-y: scroll', glm_post)
} else {
  glm_post <- glm(uds_test ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Post"), family = "binomial") %>% 
    tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                   label = list(age_group ~ "Age group",
                                race_group ~ "Race group")) %>%
    as_gt()

  div(style='height:100%; overflow-y: scroll', glm_post)
}
```

`r if(is.na(intervention_date)) {"\\end{comment}"}`

Row
-----------------------------------------------------------------------

### Predictive Parity
We measure predictive parity as the proportion of each demographic's tested subpopulation that tested positive for THC or Non-THC drugs.
<br/>**Goal**: Achieve parity in all race groups and drug detection types

Row
-----------------------------------------------------------------------

### Non-THC Logistic regression model`r if_else(is.na(intervention_date), '', '- Pre Intervention')`
```{r}
if (sum(is.na(data$pre_post_QI)) == nrow(data)) {
  glm_pre <- glm(non_thc_detect ~ race_group + age_group, data=data %>% filter(uds_test), family = "binomial") %>%
    tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                   label = list(age_group ~ "Age group",
                                race_group ~ "Race group")) %>%
  as_gt()

  div(style='height:100%; overflow-y: scroll', glm_pre)
} else {
  glm_pre <- glm(non_thc_detect ~ race_group + age_group, data=data %>% filter(uds_test) %>% filter(pre_post_QI=="Pre"), family = "binomial") %>%
    tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                   label = list(age_group ~ "Age group",
                                race_group ~ "Race group")) %>%
  as_gt()

  div(style='height:100%; overflow-y: scroll', glm_pre)
}
```

`r if(is.na(intervention_date)) {"\\begin{comment}"}`

### Non-THC Logistic regression model - Post Intervention
```{r}
if (sum(is.na(data$pre_post_QI)) == nrow(data)) {
  glm_post <- glm(non_thc_detect ~ race_group + age_group, data=data %>% filter(uds_test), family = "binomial") %>%
    tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                   label = list(age_group ~ "Age group",
                                race_group ~ "Race group")) %>%
  as_gt()

  div(style='height:100%; overflow-y: scroll', glm_post)
} else {
  glm_post <- glm(non_thc_detect ~ race_group + age_group, data=data %>% filter(uds_test) %>% filter(pre_post_QI=="Post"), family = "binomial") %>%
    tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                   label = list(age_group ~ "Age group",
                                race_group ~ "Race group")) %>%
  as_gt()

  div(style='height:100%; overflow-y: scroll', glm_post)
}
```

`r if(is.na(intervention_date)) {"\\end{comment}"}`

### THC Logistic regression model - Pre Intervention
```{r}
if (sum(is.na(data$pre_post_QI)) == nrow(data)) {
  glm_pre <- glm(thc_detect ~ race_group + age_group, data=data %>% filter(uds_test), family = "binomial") %>%
    tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                   label = list(age_group ~ "Age group",
                                race_group ~ "Race group")) %>%
  as_gt()
  
  div(style='height:100%; overflow-y: scroll', glm_pre)
} else {
  glm_pre <- glm(thc_detect ~ race_group + age_group, data=data %>% filter(uds_test) %>% filter(pre_post_QI=="Pre"), family = "binomial") %>%
    tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                   label = list(age_group ~ "Age group",
                                race_group ~ "Race group")) %>%
  as_gt()
  
  div(style='height:100%; overflow-y: scroll', glm_pre)
}
```

`r if(is.na(intervention_date)) {"\\begin{comment}"}`

### THC Logistic regression model - Post Intervention
```{r}
if (sum(is.na(data$pre_post_QI)) == nrow(data)) {
  glm_post <- glm(thc_detect ~ race_group + age_group, data=data %>% filter(uds_test), family = "binomial") %>%
    tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                   label = list(age_group ~ "Age group",
                                race_group ~ "Race group")) %>%
  as_gt()
  
  div(style='height:100%; overflow-y: scroll', glm_post)
} else {
  glm_post <- glm(thc_detect ~ race_group + age_group, data=data %>% filter(uds_test) %>% filter(pre_post_QI=="Post"), family = "binomial") %>%
    tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                   label = list(age_group ~ "Age group",
                                race_group ~ "Race group")) %>%
  as_gt()
  
  div(style='height:100%; overflow-y: scroll', glm_post)
}
```

Row
-----------------------------------------------------------------------

### Equal Outcomes for non tested mothers

We measure equal outcomes for non tested mothers using the proportion of each demographic subpopulation that were reported to CPS **without** an UDS indicating non-THC drug use. There may be other evidence not available in this data set that would be relevant to such a report, so this visual serves to illustrate the relationship between non-testing and CPS reporting only.
<br/>**Goal**: Achieve parity in all race groups

Row
-----------------------------------------------------------------------

### Non tested mothers' Logistic regression model - Pre Intervention
```{r}
# check if CPS report data is available
if(!is.na(error_cps)) {
  print(error_cps)
} else {
  if (sum(is.na(data$pre_post_QI)) == nrow(data)) {
    glm_pre <- glm(cps_report ~ race_group + age_group, data=data %>% filter(!uds_test), family = "binomial") %>%
      tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                     label = list(age_group ~ "Age group",
                                  race_group ~ "Race group")) %>%
      as_gt()
    
    div(style='height:100%; overflow-y: scroll', glm_pre)
  } else {
    glm_pre <- glm(cps_report ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Pre" & !uds_test), family = "binomial") %>%
      tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                     label = list(age_group ~ "Age group",
                                  race_group ~ "Race group")) %>%
      as_gt()
    
    div(style='height:100%; overflow-y: scroll', glm_pre)
  }
}
```

### Non tested mothers' Logistic regression model - Post Intervention
```{r}
if(!is.na(error_cps)) {
  print(error_cps)
} else {
  if (sum(is.na(data$pre_post_QI)) == nrow(data)) {
    glm_post <- glm(cps_report ~ race_group + age_group, data=data %>% filter(!uds_test), family = "binomial") %>%
      tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                     label = list(age_group ~ "Age group",
                                  race_group ~ "Race group")) %>%
      as_gt()

    div(style='height:100%; overflow-y: scroll', glm_post)
  } else {
    glm_post <- glm(cps_report ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Post" & !uds_test), family = "binomial") %>% 
      tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                     label = list(age_group ~ "Age group",
                                  race_group ~ "Race group")) %>%
      as_gt()

    div(style='height:100%; overflow-y: scroll', glm_post)
  }
}
```

### Tested mothers' Logistic regression model - Pre Intervention
```{r}
if(!is.na(error_cps)) {
  print(error_cps)
} else {
  if (sum(is.na(data$pre_post_QI)) == nrow(data)) {
    glm_pre <- glm(cps_report ~ race_group + age_group, data=data %>% filter(uds_test), family = "binomial") %>% 
      tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                     label = list(age_group ~ "Age group",
                                  race_group ~ "Race group")) %>%
      as_gt()

    div(style='height:100%; overflow-y: scroll', glm_pre)
  } else {
    glm_pre <- glm(cps_report ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Pre" & uds_test), family = "binomial") %>% 
      tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                     label = list(age_group ~ "Age group",
                                  race_group ~ "Race group")) %>%
      as_gt()

    div(style='height:100%; overflow-y: scroll', glm_pre)
  }
}
```

### Tested mothers' Logistic regression model - Post Intervention
```{r}
if(!is.na(error_cps)) {
  print(error_cps)
} else {
  if (sum(is.na(data$pre_post_QI)) == nrow(data)) {
    glm_post <- glm(cps_report ~ race_group + age_group, data=data %>% filter(uds_test), family = "binomial") %>% 
      tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                     label = list(age_group ~ "Age group",
                                  race_group ~ "Race group")) %>%
      as_gt()

    div(style='height:100%; overflow-y: scroll', glm_post)
  } else {
    glm_post <- glm(cps_report ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Post" & uds_test), family = "binomial") %>% 
      tbl_regression(add_estimate_to_reference_rows=TRUE, exponentiate = TRUE,
                     label = list(age_group ~ "Age group",
                                  race_group ~ "Race group")) %>%
      as_gt()

    div(style='height:100%; overflow-y: scroll', glm_post)
  }
}
```

`r if(is.na(intervention_date)) {"\\end{comment}"}`
