Statistics
==========================

Row
-----------------------------------------------------------------------

### Demographic Parity

We measure demographic parity using the proportion of each demographic and age subpopulation that was given drug testing.
<br/>**Goal**: Achieve parity in all race and age groups

Row
-----------------------------------------------------------------------

### Logistic regression model - Pre Intvervention
```{r}
glm_pre <- glm(uds_test ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Pre"), family = "binomial") %>% tbl_regression(add_estimate_to_reference_rows=TRUE)
glm_pre
```

### Logistic regression model - Post Intvervention
```{r}
glm_post <- glm(uds_test ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Post"), family = "binomial") %>% tbl_regression(add_estimate_to_reference_rows=TRUE)
glm_post
```

Row
-----------------------------------------------------------------------

### Predictive Parity
We measure predictive parity as the proportion of each demographic's subpopulation that tested positive for THC or Non-THC drugs.
<br/>**Goal**: Achieve parity in all race groups and drug detection types

Row
-----------------------------------------------------------------------

### Non-THC Logistic regression model - Pre Intvervention
```{r}
glm_pre <- glm(non_thc_detect ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Pre"), family = "binomial") %>% tbl_regression(add_estimate_to_reference_rows=TRUE)
glm_pre
```

### Non-THC Logistic regression model - Post Intvervention
```{r}
glm_post <- glm(non_thc_detect ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Post"), family = "binomial") %>% tbl_regression(add_estimate_to_reference_rows=TRUE)
glm_post
```

### THC Logistic regression model - Pre Intvervention
```{r}
glm_pre <- glm(thc_detect ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Pre"), family = "binomial") %>% tbl_regression(add_estimate_to_reference_rows=TRUE)
glm_pre
```

### THC Logistic regression model - Post Intvervention
```{r}
glm_post <- glm(thc_detect ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Post"), family = "binomial") %>% tbl_regression(add_estimate_to_reference_rows=TRUE)
glm_post
```

Row
-----------------------------------------------------------------------

### Equal Outcomes for non tested mothers

We measure equal outcomes for non tested mothers using the proportion of each demographic subpopulation that were reported to CPS **without** an UDS indicating non-THC drug use. There may be other evidence not available in this dataset that would be relevant to such a report, so this visual serves to illustrate the relationship between non-testing and CPS report only.
<br/>**Goal**: Achieve parity in all race groups

Row
-----------------------------------------------------------------------

### Non tested mothers' Logistic regression model - Pre Intvervention
```{r}
glm_pre <- glm(cps_report ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Pre" & !uds_test), family = "binomial") %>% tbl_regression(add_estimate_to_reference_rows=TRUE)
glm_pre
```

### Non tested mothers' Logistic regression model - Post Intvervention
```{r}
glm_post <- glm(cps_report ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Post" & !uds_test), family = "binomial") %>% tbl_regression(add_estimate_to_reference_rows=TRUE)
glm_post
```

### Tested mothers' Logistic regression model - Pre Intvervention
```{r}
glm_pre <- glm(cps_report ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Pre" & uds_test), family = "binomial") %>% tbl_regression(add_estimate_to_reference_rows=TRUE)
glm_pre
```

### Tested mothers' Logistic regression model - Post Intvervention
```{r}
glm_post <- glm(cps_report ~ race_group + age_group, data=data %>% filter(pre_post_QI=="Post" & !uds_test), family = "binomial") %>% tbl_regression(add_estimate_to_reference_rows=TRUE)
glm_post
```