Summary
==========================

Row
-----------------------------------------------------------------------

### Methods

We used four age categories: Under 25, 25 – 30, 30 – 34, and Over 34. The number of categories and precise ranges was somewhat arbitrary, but we adjusted the ranges to keep the number of individuals in each group similar in size within the Fairlabs Washington University data set.

The number of categories for the race field is reduced from the original data set
by combining all categories with fewer than 2,000 patients into a single "Other" category.
The threshold's purpose is to ensure there is enough data within each group for a robust
analysis. Mothers with multiple races were also grouped into the Other category.

We used R’s glm package to do multivariate logistic regression analyses with the age and race categories as independent variables. We repeated the analysis with a varying dependent variable and subpopulation for the metrics described below. We used the majority population as the reference group.

For local activation, we queried mothers who received our standard urine drug
screen or urine pain drug screen either ordered directly or as part of a panel.
Only drugs in our urine pain drug screen were counted as positives.
This set of drugs has some differences from those in the Fairlabs data set.
We queried drug screens up to 6 months before the date of birth and up to 30 days
after it. We only analyzed the one drug screen closest to the date of birth for each mother.


Row
-----------------------------------------------------------------------

### Demographic Parity

We measure demographic parity using the proportion of each race and age group that was given drug testing.
If the proportions are equal for all demographics, the conditions for demographic parity are met.

`r if(is.na(intervention_date)) {"\\begin{comment}"}`
**The dashed green line marks the date of QI intervention.**
`r if(is.na(intervention_date)) {"\\end{comment}"}`

Row 
-----------------------------------------------------------------------
### Visual {.no-title}
```{r}
# data visuals

## demographic parity
graph <- demo_sum %>%
  arrange(race_group,age_group, delivery_qtr)

g <- ggplot(graph, aes(x=delivery_qtr, y=perc_total, color=race_group)) +
  geom_line() +
  geom_vline(linetype="dashed", color="darkgreen", xintercept = as.numeric(intervention_date)) +
  # This geom is for visual indication of number of testing, and to add hover text 
  geom_point(aes(size = total, 
                 alpha = 0.5, 
                 text=paste('Delivery Quarter:', format(delivery_qtr, '%Y-%m'),
                            '<br>Percent of mothers tested:', label_percent()(perc_total),
                            '<br>Total number of births:', total)),
                 show.legend = FALSE) + 
  scale_color_manual(values = race_pal) +
  guides(color=guide_legend(title="Race Group")) +
  scale_y_continuous(labels = label_percent()) +
  facet_wrap(.~age_group, nrow = 2) +
  ylab('Percent of mothers tested') +
  xlab('Delivery Quarter')

ggplotly(g + theme_bw(), tooltip = c('text')) %>%
  layout(legend = list(orientation = 'h'))
```

Row
-----------------------------------------------------------------------

### Predictive Parity
We measure predictive parity using the proportion of each demographic that tested positive out of the people tested within that demographic.
If the proportions are equal the conditions of predictive parity are met.
We measure it separately for THC and Non-THC drugs.

Row 
-----------------------------------------------------------------------
### Visual {.no-title}

```{r fig.height=5}
## predictive parity
graph_non_thc <- pred_non_thc_sum %>%
  mutate(drug_cat = 'Non-THC drugs detected') %>%
  arrange(race_group, delivery_qtr)

graph_thc <- pred_thc_sum %>%
  mutate(drug_cat = 'THC detected') %>%
  arrange(race_group, delivery_qtr)

graph <- rbind(graph_non_thc, graph_thc) %>%
  arrange(drug_cat, race_group, delivery_qtr)

g <- ggplot(graph, aes(x=delivery_qtr, y=perc_total, color=race_group)) +
  geom_line() +
  geom_vline(linetype="dashed", color="darkgreen", xintercept = as.numeric(intervention_date)) +
  geom_point(aes(size = total,
                 alpha = 0.5,
                 text=paste('Delivery Quarter:', format(delivery_qtr, '%Y-%m'),
                 '<br>Percent positive:', label_percent()(perc_total),
                 '<br>Total mothers tested:', total)),
                 show.legend = FALSE) +
  facet_wrap(.~drug_cat, nrow = 2) +
  scale_color_manual(values = race_pal) +
  guides(color=guide_legend(title="Race")) +
  scale_y_continuous(labels = label_percent()) +
  ylab('Positivity rate of mothers tested') +
  xlab('Delivery Quarter')

ggplotly(g + theme_bw(), tooltip = c('text')) %>%
  layout(legend = list(orientation = 'h'))
```

`r if(is.na(intervention_date)) {"\\begin{comment}"}`

Row
-----------------------------------------------------------------------

### Equalized Odds

We measure equalized odds using the proportion of each demographic and age subpopulation that was given drug testing with a relevant order indication such as "Substance use during pregnancy, excluding marijuana" and "History of opioids prescribed during pregnancy".
<br/>**Goal**: Achieve parity in all race and age groups

Row 
-----------------------------------------------------------------------
### Visual {.no-title}
```{r}
# check if order indication data is available
if(!is.na(error_ord)) {
  print(error_ord)
} else {
  ## equalized odds

  graph <- pivot_longer(
    data = equal_odds_wide%>%
      select(c("race_group","age_group","pre_post_QI",'FPR','TPR')), cols = c('FPR','TPR'), names_to = "type", values_to = "value") %>%
           filter(pre_post_QI == 'Post') %>%
    # add summary of the total number of mothers tested
    merge(equal_odds %>%
    group_by(race_group,pre_post_QI,age_group) %>%
    summarize(total=sum(n)), by = c("race_group","pre_post_QI","age_group")) %>%
    mutate(type = if_else(type=="FPR", 'Percent of negative results with revelant order indication', 'Percent of positive results with revelant order indication'))

  g <- ggplot(graph, aes(x=race_group,
                         y=value,
                         fill=age_group,
                         text= paste('Total number of mothers tested:', total,
                                     '<br>Percent of total:', label_percent()(value)))) +
    geom_col(position='dodge')+
    facet_grid(.~type, labeller = label_wrap_gen(width = 40)) +
    scale_y_continuous(labels = label_percent()) +
    scale_fill_manual(values = age_pal) +
    guides(fill=guide_legend(title="Age Group")) +
    ylab('Percent') +
    xlab('Race Group')

  ggplotly(g + theme_bw(), tooltip = 'text') %>%
    layout(legend = list(orientation = 'h'))
}
```

Row
-----------------------------------------------------------------------

### General Group Equity

We measure general group equity using the proportion of each demographic and age subpopulation that received intervention for the correct event.<br/>
Equation: (TP+FP)/(TP+FN)<br/>
Definition:<br/>
- True positive is # of patients tested **positive** for non THC substance and **was reported** to CPS<br/>
- False positive is # of patients tested **negative** for non THC substance and **was reported** to CPS<br/>
- True negative is # of patients tested **negative** for non THC substance and **wasn’t reported** to CPS<br/>
- False negative is # of patients tested **positive** for non THC substance and **was reported** to CPS<br/>
**Goal**: Achieve as close to a ratio of 1 as possible so that a group is not under-served (ratio < 1) or over-served (ratio > 1)

Row 
-----------------------------------------------------------------------
### Visual {.no-title}
```{r}
# check if CPS report data is available
if(!is.na(error_cps)) {
  print(error_cps)
} else {
  ## group benefit equality 
  graph <- group_benefit_wide %>%
    filter(race_group!='Other') %>%
    merge(group_benefit %>%
    group_by(race_group, age_group, pre_post_QI) %>%
    # add summary of the total number of mothers tested
    summarize(total=sum(n)) %>%
      ungroup(), by = c("race_group", "age_group", "pre_post_QI")) %>%
     mutate(pre_post_QI = factor(if_else(pre_post_QI=='Pre', 'Pre QI Intervention', 'Post QI Intervention'), levels=c('Pre QI Intervention', 'Post QI Intervention')))

  g<-ggplot(graph, aes(x=race_group,
                       y=ratio,
                       fill=age_group,
                       text=paste('General Group Equity Ratio:', ratio,
                                  '<br>Total number of mothers:', total))) +
    geom_col(position='dodge')+
    geom_hline(yintercept = 1) +
    scale_fill_manual(values = age_pal) +
    facet_grid(.~pre_post_QI) +
    guides(fill=guide_legend(title="Age Group")) +
    ylab('General Group Equity Ratio') +
    xlab('Race Group')

  ggplotly(g + theme_bw(), tooltip = 'text') %>%
    layout(legend = list(orientation = 'h'))
}
```

Row
-----------------------------------------------------------------------

### Equal Outcomes for non tested mothers

We measure equal outcomes for non tested mothers using the proportion of each demographic subpopulation that were reported to CPS **without** an UDS indicating non-THC drug use. There may be other evidence not available in this dataset that would be relevant to such a report, so this visual serves to illustrate the relationship between non-testing and CPS report only.
<br/>**Goal**: Achieve parity in all race groups

Row 
-----------------------------------------------------------------------
### Visual {.no-title}
```{r}
if(!is.na(error_cps)) {
  print(error_cps)
} else {
  ## equal outcomes for non tested mothers
  graph <- equal_out %>% filter(cps_report & !uds_test)
  
  g<-ggplot(graph, aes(x=delivery_qtr, y=perc_total, color=race_group)) +
    geom_line()+
    geom_vline(linetype="dashed", color="darkgreen", xintercept = as.numeric(intervention_date)) +
    scale_color_manual(values = race_pal) +
    geom_point(aes(size = total,
                   alpha = 0.5,
                   text=paste('Percent of mothers reported to CPS:', label_percent()(perc_total),
                              '<br>Total number of births:', total)), show.legend = FALSE) +
    guides(color=guide_legend(title="Race"))+
    scale_y_continuous(labels = label_percent()) +
    ylab('Percent of mothers reported to CPS') +
    xlab('Delivery Quarter')
  
  ggplotly(g + theme_bw(), tooltip = 'text') %>%
    layout(legend = list(orientation = 'h'))
}
```

Row
-----------------------------------------------------------------------

### Equal Outcomes for tested mothers

We measure equal outcomes for non tested mothers using the proportion of each demographic subpopulation that were reported to CPS **with** an UDS indicating non-THC drug use. There may be other evidence not available in this dataset that would be relevant to such a report, so this visual serves to illustrate the relationship between testing and CPS report only.
<br/>**Goal**: Achieve parity in all race groups

Row 
-----------------------------------------------------------------------
### Visual {.no-title}
```{r}
if(!is.na(error_cps)) {
  print(error_cps)
} else {
  ## equal outcomes for tested mothers
  graph <- equal_out %>%
    filter(cps_report & uds_test) %>%
    mutate(non_thc_detect = if_else(non_thc_detect, 'Non-THC drugs detected', 'No Non-THC drugs detected'))
  

  g<-ggplot(graph, aes(x=delivery_qtr, y=perc_total, color=race_group)) +
    geom_line()+
    geom_vline(linetype="dashed", color="darkgreen", xintercept = as.numeric(intervention_date)) +
    geom_point(aes(size = total,
                   alpha = 0.5,
                   text=paste('Delivery Quarter:', format(delivery_qtr, '%Y-%m'),
                              '<br>Percent of mothers tested:', label_percent()(perc_total),
                              '<br>Total number of births:', total)), show.legend = FALSE) +
    facet_grid(.~non_thc_detect)+
    scale_color_manual(values = race_pal) +
    guides(color=guide_legend(title="Race")) +
    scale_y_continuous(labels = label_percent()) +
    ylab('Percent of mothers reported to CPS') +
    xlab('Delivery Quarter')
  
  ggplotly(g + theme_bw(), tooltip = 'text') %>%
    layout(legend = list(orientation = 'h'))
}
```
`r if(is.na(intervention_date)) {"\\end{comment}"}`
