Summary
==========================

Row
-----------------------------------------------------------------------

### Methods

We used three categories for the race field: Black or African American, White and Other. The Other category includes all other racial groups in the dataset, mothers with an unspecified race and those with multiple races. None of these categories were analyzed individually because the Other category only makes up 10% of the datapoints in total, so there would be insufficient data for a robust analysis.
 
We used four age categories: Under 25, 25 – 30, 30 – 34, and Over 34. The number of categories and precise ranges was somewhat arbitrary, but we adjusted the ranges to keep the number of individuals in each group similar in size.

We used R’s glm package to do multivariate logistic regression analyses with the age and race categories as independent variables. We repeated the analysis with a varying dependent variable and subpopulation for the metrics described below.

Row
-----------------------------------------------------------------------

### Demographic Parity

We measure demographic parity using the proportion of each race and age group that was given drug testing.
If the proportions are equal for all demographics, the conditions for demographic parity are met.
If no intervention date was given, then the same table will show for both pre and post intervention sections.

**The dashed green line marks the date of QI intervention.**

Row 
-----------------------------------------------------------------------
### Visual {.no-title}
```{r}
# data visuals

## demographic parity
graph <- demo_sum %>%
  filter(uds_test) %>%
  arrange(race_group,age_group, delivery_qtr)

g <- ggplot(graph, aes(x=delivery_qtr, y=perc_total, color=race_group)) +
  geom_line() +
  geom_vline(linetype="dashed", color="darkgreen", xintercept = as.numeric(intervention_date)) +
  # This geom is for visual indication of number of testing, and to add hover text 
  geom_point(aes(size = total, 
                 alpha = 0.5, 
                 text=paste('Delivery Quarter:', format(delivery_qtr, '%Y-%m'),
                            '<br>Percent of mothers tested:', label_percent()(perc_total),
                            '<br>Total number of births:', total)),
                 show.legend = FALSE) + 
  scale_color_manual(values = race_pal) +
  guides(color=guide_legend(title="Race Group")) +
  scale_y_continuous(labels = label_percent()) +
  facet_wrap(.~age_group, nrow = 2) +
  ylab('Percent of mothers tested') +
  xlab('Delivery Quarter')

ggplotly(g, tooltip = c('text')) %>%
  layout(legend = list(orientation = 'h'))
```

Row
-----------------------------------------------------------------------

### Predictive Parity
We measure predictive parity using the proportion of each demographic's subpopulation that tested positive out of the people tested.
If the proportions are equal the conditions of predictive partity are met.
We measure it separately for THC or Non-THC drugs.

Row 
-----------------------------------------------------------------------
### Visual {.no-title}

```{r fig.height=5}
## predictive parity
graph_non_thc <- pred_non_thc_sum %>%
  filter(non_thc_detect) %>%
  mutate(drug_cat = 'Non-THC drugs detected') %>%
  select(-c(non_thc_detect)) %>%
  arrange(race_group, delivery_qtr)

graph_thc <- pred_thc_sum %>%
  filter(thc_detect) %>%
  mutate(drug_cat = 'THC detected') %>%
  select(-c(thc_detect)) %>%
  arrange(race_group, delivery_qtr)

graph <- rbind(graph_non_thc, graph_thc) %>%
  arrange(race_group, delivery_qtr)

g <- ggplot(graph, aes(x=delivery_qtr, y=perc_total, color=race_group)) +
  geom_line() +
  geom_vline(linetype="dashed", color="darkgreen", xintercept = as.numeric(intervention_date)) +
  geom_point(aes(size = total,
                 alpha = 0.5,
                 text=paste('Delivery Quarter:', format(delivery_qtr, '%Y-%m'),
                 '<br>Percent of mothers tested:', label_percent()(perc_total),
                 '<br>Total number of births:', total)),
                 show.legend = FALSE) +
  facet_wrap(.~drug_cat, nrow = 2) +
  scale_color_manual(values = race_pal) +
  guides(color=guide_legend(title="Race")) +
  scale_y_continuous(labels = label_percent()) +
  ylab('Percent of mothers tested') +
  xlab('Delivery Quarter')

ggplotly(g, tooltip = c('text')) %>%
  layout(legend = list(orientation = 'h'))
```

Row
-----------------------------------------------------------------------

### Equalized Odds

We measure equalized odds using the proportion of each demographic and age subpopulation that was given drug testing with a relevant order indication such as "Substance use during pregnancy, excluding marijuana" and "History of opioids prescribed during pregnancy".
<br/>**Goal**: Achieve parity in all race and age groups

Row 
-----------------------------------------------------------------------
### Visual {.no-title}
```{r}
# check if order indication data is available
if(!is.na(error_ord)) {
  print(error_ord)
} else {
  ## equalized odds

  graph <- pivot_longer(
    data = equal_odds_wide%>%
      select(c("race_group","age_group","pre_post_QI",'FPR','TPR')), cols = c('FPR','TPR'), names_to = "type", values_to = "value") %>%
           filter(pre_post_QI == 'Post') %>%
    # add summary of the total number of mothers tested
    merge(equal_odds %>%
    group_by(race_group,pre_post_QI,age_group) %>%
    summarize(total=sum(n)), by = c("race_group","pre_post_QI","age_group")) %>%
    mutate(type = if_else(type=="FPR", 'Percent of negative results with revelant order indication', 'Percent of positive results with revelant order indication'))

  g <- ggplot(graph, aes(x=race_group,
                         y=value,
                         fill=age_group,
                         text= paste('Total number of mothers tested:', total,
                                     '<br>Percent of total:', label_percent()(value)))) +
    geom_col(position='dodge')+
    facet_grid(.~type, labeller = label_wrap_gen(width = 40)) +
    scale_y_continuous(labels = label_percent()) +
    scale_fill_manual(values = age_pal) +
    guides(fill=guide_legend(title="Age Group")) +
    ylab('Percent') +
    xlab('Race Group')

  ggplotly(g, tooltip = 'text') %>%
    layout(legend = list(orientation = 'h'))
}
```

Row
-----------------------------------------------------------------------

### General Group Equity

We measure general group equity using the proportion of each demographic and age subpopulation that received intervention for the correct event.<br/>
Equation: (TP+FP)/(TP+FN)<br/>
Definition:<br/>
- True positive is # of patients tested **positive** for non THC substance and **was reported** to CPS<br/>
- False positive is # of patients tested **negative** for non THC substance and **was reported** to CPS<br/>
- True negative is # of patients tested **negative** for non THC substance and **wasn’t reported** to CPS<br/>
- False negative is # of patients tested **positive** for non THC substance and **was reported** to CPS<br/>
**Goal**: Achieve as close to a ratio of 1 as possible so that a group is not under-served (ratio < 1) or over-served (ratio > 1)

Row 
-----------------------------------------------------------------------
### Visual {.no-title}
```{r}
# check if CPS report data is available
if(!is.na(error_cps)) {
  print(error_cps)
} else {
  ## group benefit equality 
  graph <- group_benefit_wide %>%
    filter(race_group!='Other') %>%
    merge(group_benefit %>%
    group_by(race_group, age_group, pre_post_QI) %>%
    # add summary of the total number of mothers tested
    summarize(total=sum(n)) %>%
      ungroup(), by = c("race_group", "age_group", "pre_post_QI")) %>%
     mutate(pre_post_QI = factor(if_else(pre_post_QI=='Pre', 'Pre QI Intervention', 'Post QI Intervention'), levels=c('Pre QI Intervention', 'Post QI Intervention')))

  g<-ggplot(graph, aes(x=race_group,
                       y=ratio,
                       fill=age_group,
                       text=paste('General Group Equity Ratio:', ratio,
                                  '<br>Total number of mothers:', total))) +
    geom_col(position='dodge')+
    geom_hline(yintercept = 1) +
    scale_fill_manual(values = age_pal) +
    facet_grid(.~pre_post_QI) +
    guides(fill=guide_legend(title="Age Group")) +
    ylab('General Group Equity Ratio') +
    xlab('Race Group')

  ggplotly(g, tooltip = 'text') %>%
    layout(legend = list(orientation = 'h'))
}
```

Row
-----------------------------------------------------------------------

### Equal Outcomes for non tested mothers

We measure equal outcomes for non tested mothers using the proportion of each demographic subpopulation that were reported to CPS **without** an UDS indicating non-THC drug use. There may be other evidence not available in this dataset that would be relevant to such a report, so this visual serves to illustrate the relationship between non-testing and CPS report only.
<br/>**Goal**: Achieve parity in all race groups

Row 
-----------------------------------------------------------------------
### Visual {.no-title}
```{r}
if(!is.na(error_cps)) {
  print(error_cps)
} else {
  ## equal outcomes for non tested mothers
  graph <- equal_out %>% filter(cps_report & !uds_test)
  
  g<-ggplot(graph, aes(x=delivery_qtr, y=perc_total, color=race_group)) +
    geom_line()+
    geom_vline(linetype="dashed", color="darkgreen", xintercept = as.numeric(intervention_date)) +
    scale_color_manual(values = race_pal) +
    geom_point(aes(size = total,
                   alpha = 0.5,
                   text=paste('Percent of mothers reported to CPS:', label_percent()(perc_total),
                              '<br>Total number of births:', total)), show.legend = FALSE) +
    guides(color=guide_legend(title="Race"))+
    scale_y_continuous(labels = label_percent()) +
    ylab('Percent of mothers reported to CPS') +
    xlab('Delivery Quarter')
  
  ggplotly(g, tooltip = 'text') %>%
    layout(legend = list(orientation = 'h'))
}
```

Row
-----------------------------------------------------------------------

### Equal Outcomes for tested mothers

We measure equal outcomes for non tested mothers using the proportion of each demographic subpopulation that were reported to CPS **with** an UDS indicating non-THC drug use. There may be other evidence not available in this dataset that would be relevant to such a report, so this visual serves to illustrate the relationship between testing and CPS report only.
<br/>**Goal**: Achieve parity in all race groups

Row 
-----------------------------------------------------------------------
### Visual {.no-title}
```{r}
if(!is.na(error_cps)) {
  print(error_cps)
} else {
  ## equal outcomes for tested mothers
  graph <- equal_out %>%
    filter(cps_report & uds_test) %>%
    mutate(non_thc_detect = if_else(non_thc_detect, 'Non-THC drugs detected', 'No Non-THC drugs detected'))
  
  g<-ggplot(graph, aes(x=delivery_qtr, y=perc_total, color=race_group)) +
    geom_line()+
    geom_vline(linetype="dashed", color="darkgreen", xintercept = as.numeric(intervention_date)) +
    geom_point(aes(size = total,
                   alpha = 0.5,
                   text=paste('Delivery Quarter:', format(delivery_qtr, '%Y-%m'),
                              '<br>Percent of mothers tested:', label_percent()(perc_total),
                              '<br>Total number of births:', total)), show.legend = FALSE) +
    facet_grid(.~non_thc_detect)+
    scale_color_manual(values = race_pal) +
    guides(color=guide_legend(title="Race")) +
    scale_y_continuous(labels = label_percent()) +
    ylab('Percent of mothers reported to CPS') +
    xlab('Delivery Quarter')
  
  ggplotly(g, tooltip = 'text') %>%
    layout(legend = list(orientation = 'h'))
}
```
